---
title: "Camping is In-Tents: MacLeish Site Recommendations"
author: Rachel Moskowitz, Sonia Garfinkel, and Greta Mundt
date: April 13, 2018
output: 
  html_document:
    df_print: paged
    code_folding: hide
    theme: "journal"
---

#####Problem statement: 
MacLeish currently only has two campsites, one large group site close to the building, and a remote campsite with two tent platforms a mile away. There is a need for an additional campsite at the field station. There is an interest in developing a new campsite half a mile away from the parking area, within 200' of a stream or water source, 500' away from any research area or Challenge Course element, in a forest unlike the forest of the other two campsites, and relatively flat. All of these components must be present in a new campsite for consideration.


#####Campsite recommendation
Our project proposes two new potential campsite locations for MacLeish. Our final recommendations for new campsite locations are shown in our map below with blue pop up identifiers. We used a github repository in order to keep track of and evaluate the spatial data necessary for making our recommendations [^1]. These locations were chosen based on the following criteria and spatial analysis procedures.
1. Campsites must be located in a forest unlike the forest of the other two campsites. The existing campsites are located in an Old Field White Pine Forest and a Sugar Maple Forest, which can be found by clicking on the vegetation near these popups on the map below. We knew we could not place our new proposed campsites in either of these vegetation types. This limited our proposed campsites. We chose to place the campsites within the (name two other vegetation types)
2. The ideal location for a campsite is within 200 feet of a stream or other water source, so the location can be near potable water. To find areas within 200 feet of a water source we used the buffer tool and were able to find areas next to streams.
3. Campsites cannot be located within a 500 foot radius of any research station or challenge course element. This allows research areas and challenge course users to function uninterrupted. To find this, we used a union to join the challenge course and research station layers, and then created a buffer that went around both types of sites. 
4. For convenience, a campsite must be located within a half mile of the parking lot at the field station. We created a buffer to cites that fit this criteria. Both of our campsites fall within the half mile radius of the parking lot.
5. Because it is uncomfortable and unsafe to sleep on an incline, we took elevation data into account to find relatively flat locations for our campsites. 
After taking vegetation type, water sources, research station, challenge course element, parking lot locations, and elevation into account, we were able to narrow our search to a handful of possible locations for the new campsites. We then narrowed our choices down to two proposed campsite locations. These locations are shown as blue popups in the second provided map.


```{r,  message = FALSE, warning = FALSE}
library(tidyverse)
library(sf)
library(macleish)
library(leaflet)
```

```{r}
#we added the existing group campsites as data.frames
group_campsite1 <- data.frame(lat = 42.450976, lon = -72.678154)
group_campsite2 <-data.frame(lat = 42.458549, lon = -72.679581)
#adding the parking lot as a data.frame
parking_lot <-data.frame(lat = 42.448013, lon = -72.680663)

#transforming parking lot data.frame to an sf object with defined projection
parking_sf <- parking_lot %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326)
```


```{r, message = FALSE, warning = FALSE}
#projection for our buffers
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

#making a buffer of 200' for the stream, have to convert feet to meters for the distqnce and put it all in the correct projection system 
stream_buffer <- macleish_layers[["streams"]] %>%
  st_transform(proj4_aea) %>%
   st_buffer(dist = 60.96) %>%
  st_transform(4326)

#this is the research buffer, with conversions for meters 
research_buffers <- macleish_layers[["research"]] %>%
   st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

#get rid of overlap with st_union()
research_buffer <- st_geometry(research_buffers)
union1 <- st_union(research_buffer)

#500' buffer around challenge courses
challenge_buffers <- macleish_layers[["challenge_courses"]] %>%
   st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

#dissolve overlap with st_union()
challenge_buffer <- st_geometry(challenge_buffers)
union2 <- st_union(challenge_buffer)

#half a mile buffer around our parking object
parking_buffer <- parking_sf %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 804.7) %>%
  st_transform(4326)

#use st_union() to group challenge course buffer and research buffers together
res_challenge_union <- st_union(union1, union2)
```

Interactive map with buffers: research
This map shows.... (explain the buffers etc) has to be within the green and blue buffers but outside of the red buffers
  
```{r}
#interactive leaflet map w/ macleish_layers and own data added
leaflet() %>%
  addTiles() %>%

#how we showed the wetlands with popups
   addPolygons(data = macleish_layers[["wetlands"]], 
              color = "blue", 
              fillOpacity = 0.8, weight = 0.1, 
              popup = ~IT_VALDESC) %>%
  
#add trails, streams, boundary, and contours as layers
  addPolylines(data = macleish_layers[["trails"]], color = "brown", weight = 2) %>%
  
  addPolylines(data = macleish_layers[["streams"]], color = "blue", weight = 3) %>%
  
  addPolygons(data = macleish_layers[["boundary"]], stroke = TRUE, color = "black", fill = NA, weight = 2, opacity = 2) %>%
  
  addPolylines(data = macleish_layers[["contours_3m"]], color = "black", weight = 1) %>%
  
#add existing campsites and parking lot as popups
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite1, popup = "Current Group Campsite") %>%
  
  addMarkers(lng= ~lon, lat = ~lat, data = parking_lot, popup = "MacLeish Parking Lot") %>%
  
  addMarkers (lng = ~lon, lat = ~lat, data = group_campsite2, popup = "Current Group Campsite (Remote)") %>%

#add stream buffer 
  addPolygons(data = stream_buffer, stroke = TRUE, weight = 1, fill = TRUE)  %>%
  
#adding the buffer: union of research and challenge course
  addPolygons(data = res_challenge_union, fill = TRUE, fillOpacity = 0.5, color = "red", stroke = FALSE) %>%
  
  addPolygons(data = parking_buffer, fill = TRUE, color = "green", stroke = FALSE)
```


Our second map shows the two campsites we have proposed. Input: description of this map

also explain differences in vegetation type

```{r}
#add two new campsites as data.frames
new_campsite1 <-data.frame(lat= 42.445917, lon = -72.679673)
new_campsite2 <-data.frame(lat = 42.448911, lon = -72.673964)

#creating a color palette for forests
forest_pal <-colorNumeric("Greens", macleish_layers[["forests"]]$Sheet1__Ve)

#leaflet- map #2 with tiles and base polylines and polygons and vegetation
leaflet() %>%
  addTiles() %>%
  
addPolygons(data = macleish_layers[["forests"]], 
              color = ~forest_pal(Sheet1__Ve), 
              fillOpacity = 0.8, weight = 0.1, 
              popup = ~Sheet1__Na) %>%
  
    addPolylines(data = macleish_layers[["trails"]], color = "brown", weight = 1) %>%
  
  addPolylines(data = macleish_layers[["streams"]], color = "blue", weight = 3) %>%
  
  addPolygons(data = macleish_layers[["boundary"]], stroke = TRUE, color = "black", fill = NA, weight = 1, opacity = 2) %>%
  
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite1, popup = "Current Group Campsite") %>%
  
  addMarkers(lng= ~lon, lat = ~lat, data = parking_lot, popup = "MacLeish Parking Lot") %>%
  
  addMarkers (lng = ~lon, lat = ~lat, data = group_campsite2, popup = "Current Group Campsite (Remote)") %>%

  #addition of two proposed sites w/out any buffers
      addMarkers( data = new_campsite1, popup = "Proposed Group Campsite #1") %>%

    addMarkers(data = new_campsite2, popup = "Proposed Group Campsite #2")
  
  # %>% addLegend(pal = forest_pal, values = ~Sheet1__Ve, title = "Vegetation Type", opacity = 1)
```


#####Resources necessary to implement this recommendation

With our findings, Smith College and the Macleish Field Station should plan on creating more campsites over the summer. However, there are many elements to be considerred beyond the placement of the campsites. First, the field station must consider the cost of the campsite. After talking to Reid Bertone-Johnson we learned that it costs around 200 dollars to build a standard tent platform and picnic table set up, and around 3,000 dollars to invest in a lean-to structure. The Field Station does not anticipate building another lean-to because of the lofty cost and labor. It would likely take a weekend to build a tent platform and picnic table, using labor from people already employed by the Center for the Environment, Ecological Design, and Sustainability. The only environmental concern is the location in proximity to a stream. The campsite should be close to a stream, but not too close as to cause erosion. The Field Station does not take run-off into account when building campsites as the area of a campsite is generally not large enough to cause any run-off issues. There are not any major roadblocks at this moment. The Field Station has the resources neccessary to build new campsites. 


[^1]: [Link to github repository](https://github.com/rmoskowitz/mp3)