---
title: "Mini Project 3"
author: Rachel Moskowitz, Sonia Garfinkel, and Greta Mundt
output: 
  html_document:
    df_print: paged
    code_folding: hide
    theme: "journal"
---

#####Problem statement: 
MacLeish currently has two campsites - one large group site closer to the building and one remote campsite with two tent platforms about one mile from the parking area. We would like to develop one additional campsite that is approximately half a mile walk from the parking area, within 200’ of a stream or other source of water, in forest that is unlike the forest in the two other campsites, relatively flat, and at least 500’ from any research area or any element of the Challenge Course. Propose two new campsite locations for our consideration.



#####Campsite recommendation
Propose TWO campsite locations == make markers on the MAP
make a buffer around a half mile walk from the parking area
buffer around 200' of a stream of water source
in forest unlike the other forest types -- not in an Old Field White Pine Forest OR a Sugar Maple Forest

We used a github repository [^1]

```{r,  message = FALSE, warning = FALSE}
library(tidyverse)
library(sf)
library(macleish)
library(leaflet)
```

```{r}
group_campsite1 <- data.frame(lat = 42.450976, lon = -72.678154)
group_campsite2 <-data.frame(lat = 42.458549, lon = -72.679581)
parking_lot <-data.frame(lat = 42.448013, lon = -72.680663)
```


```{r}
leaflet() %>%
  addTiles() %>%
  
  addPolygons(data = macleish_layers[["forests"]], color = "green", opacity = 5,  weight = 1, popup = ~Sheet1__Na) %>%
  
   addPolygons(data = macleish_layers[["wetlands"]], 
              color = "blue", 
              fillOpacity = 0.8, weight = 0.1, 
              popup = ~IT_VALDESC) %>%
  
    addPolygons(data = macleish_layers[["research"]], color = "red", weight = 1, opacity = 2) %>%
  addCircleMarkers(data = macleish_layers[["challenge_courses"]], color = "red", weight = 1, opacity = 2) %>%
  addPolylines(data = macleish_layers[["trails"]], color = "brown", weight = 1) %>%
  addPolylines(data = macleish_layers[["streams"]], color = "blue", weight = 3) %>%
  addPolygons(data = macleish_layers[["boundary"]], stroke = TRUE, color = "black", fill = NA, weight = 2, opacity = 2) %>%
  addPolylines(data = macleish_layers[["contours_3m"]], color = "black", weight = 1) %>%
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite1, popup = "Current Group Campsite") %>%
  addMarkers(lng= ~lon, lat = ~lat, data = parking_lot, popup = "MacLeish Parking Lot") %>%
  addMarkers (lng = ~lon, lat = ~lat, data = group_campsite2, popup = "Current Group Campsite (Remote)")
```


#####Resources necessary to implement this recommendation
- These two campsites will cost
- This will take....
- Concerns about environmental impact
- major roadblocks...


- include relevant external information (look at macleish info)


[^1]: [Link to github repository](https://github.com/rmoskowitz/mp3)