---
title: "Camping is In-Tents: MacLeish Site Recommendations"
author: Rachel Moskowitz, Sonia Garfinkel, and Greta Mundt
date: April 13, 2018
output: 
  html_document:
    df_print: paged
    code_folding: hide
    theme: "journal"
---


####Problem statement
MacLeish currently only has two campsites. There is a need for an additional campsite at the field station. There is an interest in developing a new campsite half a mile away from the parking area, within 200' of a stream or water source, 500' away from any research area or Challenge Course element, in a forest unlike the forest of the other two campsites, and relatively flat. 


####Campsite recommendation
Our project proposes two new potential campsite locations for MacLeish. Our final recommendations for new campsite locations are shown in our map below with blue pop up identifiers. We used a github repository in order to keep track of and evaluate the spatial data necessary for making our recommendations [^1]. These locations were chosen based on the following criteria.


1. **Forests:**
Campsites must be located in a forest unlike the forest of the other two campsites. The existing campsites are located in an Old Field White Pine Forest and a Sugar Maple Forest, which can be found by clicking on the vegetation near these popups on the map below. We chose to place the campsites within the Sugar Maple Forest and the Hemlock Northern Hardwoods Forest instead.
   
   
   2. **Water source:** The ideal location for a campsite is within 200 feet of a stream. To find areas within 200 feet of a water source we used the buffer tool and were able to find areas next to streams. 
  
  
   3. **Research and challenge course:** Campsites cannot be located within a 500 foot radius of any research station or challenge course element. This allows research areas and challenge course users to function uninterrupted. To find this, we created buffers around these sites, and then used a union to join the buffers. 
   
   
4. **Parking lot:** For convenience, a campsite must be located within a half mile of the parking lot at the field station. We created a buffer to sites that fit this criteria. 


5. **Elevation:** Because it is uncomfortable and unsafe to sleep on an incline, we took elevation data into account to find relatively flat locations for our campsites. 


After taking vegetation type, water sources, research station, challenge course element, parking lot locations, and elevation into account, we were able to narrow our search to a couple of possible locations for the new campsites. 


```{r,  message = FALSE, warning = FALSE}
library(tidyverse)
library(sf)
library(macleish)
library(leaflet)
```

```{r}
#we added the existing group campsites as data.frames
group_campsite1 <- data.frame(lat = 42.450976, lon = -72.678154)
group_campsite2 <-data.frame(lat = 42.458549, lon = -72.679581)
#adding the parking lot as a data.frame
parking_lot <-data.frame(lat = 42.448013, lon = -72.680663)

#transforming parking lot data.frame to an sf object with defined projection
parking_sf <- parking_lot %>%
  st_as_sf(coords = c("lon", "lat"), crs = 4326)
```


```{r, message = FALSE, warning = FALSE}
#projection for our buffers
proj4_aea <- "+proj=aea +lat_1=29.5 +lat_2=45.5 +lat_0=37.5 +lon_0=-96 +x_0=0 +y_0=0 +ellps=GRS80 +datum=NAD83 +units=m +no_defs"

#making a buffer of 200' for the stream, have to convert feet to meters for the distqnce and put it all in the correct projection system 
stream_buffer <- macleish_layers[["streams"]] %>%
  st_transform(proj4_aea) %>%
   st_buffer(dist = 60.96) %>%
  st_transform(4326)

#this is the research buffer, with conversions for meters 
research_buffers <- macleish_layers[["research"]] %>%
   st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

#get rid of overlap with st_union()
research_buffer <- st_geometry(research_buffers)
union1 <- st_union(research_buffer)

#500' buffer around challenge courses
challenge_buffers <- macleish_layers[["challenge_courses"]] %>%
   st_transform(proj4_aea) %>%
  st_buffer(dist = 152.4) %>%
  st_transform(4326)

#dissolve overlap with st_union()
challenge_buffer <- st_geometry(challenge_buffers)
union2 <- st_union(challenge_buffer)

#half a mile buffer around our parking object
parking_buffer <- parking_sf %>%
  st_transform(proj4_aea) %>%
  st_buffer(dist = 804.7) %>%
  st_transform(4326)

#use st_union() to group challenge course buffer and research buffers together
res_challenge_union <- st_union(union1, union2)
```

####Map #1: Buffers and contours
Our first map displayed below shows our process for determining where our campsite recommendations will go. The red buffer shows areas where our campsites cannot be located, because they are too close to a challenge course or research station. Our proposed sites must be located at an intersection between the green buffer and the blue buffers. These areas indicate locations that are close enough to the parking lot and within reasonable distance of a stream. This map also shows elevation data through contours, in order to understand which areas are relatively flat. Click on the blue pop-up markers to find where the existing campsites and parking lot are all located.
  
```{r}
#interactive leaflet map w/ macleish_layers and own data added
leaflet() %>%
  addTiles() %>%

#how we showed the wetlands with popups
   addPolygons(data = macleish_layers[["wetlands"]], 
              color = "blue", 
              fillOpacity = 0.8, weight = 0.1, 
              popup = ~IT_VALDESC) %>%
  
#add trails, streams, boundary, and contours as layers
  addPolylines(data = macleish_layers[["trails"]], color = "brown", weight = 2) %>%
  
  addPolylines(data = macleish_layers[["streams"]], color = "blue", weight = 3) %>%
  
  addPolygons(data = macleish_layers[["boundary"]], stroke = TRUE, color = "black", fill = NA, weight = 2, opacity = 2) %>%
  
  addPolylines(data = macleish_layers[["contours_3m"]], color = "black", weight = 1) %>%
  
#add existing campsites and parking lot as popups
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite1, popup = "Current Group Campsite") %>%
  
  addMarkers(lng= ~lon, lat = ~lat, data = parking_lot, popup = "MacLeish Parking Lot") %>%
  
  addMarkers (lng = ~lon, lat = ~lat, data = group_campsite2, popup = "Current Group Campsite (Remote)") %>%

#add stream buffer 
  addPolygons(data = stream_buffer, stroke = TRUE, weight = 1, fill = TRUE)  %>%
  
#adding the buffer: union of research and challenge course
  addPolygons(data = res_challenge_union, fill = TRUE, fillOpacity = 0.5, color = "red", stroke = FALSE) %>%
  
  addPolygons(data = parking_buffer, fill = TRUE, color = "green", stroke = FALSE)
```

####Map #2: Vegetation and recommendations
The two campsites we proposed are located in new vegetation types, are in relatively flat areas, within 200' from a water source, and outside of the buffers around the challenge course elements and research stations. Click on different parts of the map to find the vegetation type at that location. You can also click on the popups to see the existing campsites and our recommendation sites. 

```{r}
#add two new campsites as data.frames
new_campsite1 <-data.frame(lat= 42.445917, lon = -72.679673)
new_campsite2 <-data.frame(lat = 42.448911, lon = -72.673964)

#creating a color palette for forests
forest_pal <-colorNumeric("Greens", macleish_layers[["forests"]]$Sheet1__Ve)

#leaflet- map #2 with tiles and base polylines and polygons and vegetation
leaflet() %>%
  addTiles() %>%
  
addPolygons(data = macleish_layers[["forests"]], 
              color = ~forest_pal(Sheet1__Ve), 
              fillOpacity = 0.8, weight = 0.1, 
              popup = ~Sheet1__Na) %>%
  
    addPolylines(data = macleish_layers[["trails"]], color = "brown", weight = 1) %>%
  
  addPolylines(data = macleish_layers[["streams"]], color = "blue", weight = 3) %>%
  
  addPolygons(data = macleish_layers[["boundary"]], stroke = TRUE, color = "black", fill = NA, weight = 1, opacity = 2) %>%
  
  addMarkers(lng = ~lon, lat = ~lat, data = group_campsite1, popup = "Current Group Campsite") %>%
  
  addMarkers(lng= ~lon, lat = ~lat, data = parking_lot, popup = "MacLeish Parking Lot") %>%
  
  addMarkers (lng = ~lon, lat = ~lat, data = group_campsite2, popup = "Current Group Campsite (Remote)") %>%

  #addition of two proposed sites w/out any buffers
      addMarkers( data = new_campsite1, popup = "Proposed Group Campsite #1") %>%

    addMarkers(data = new_campsite2, popup = "Proposed Group Campsite #2") 
  
  # addLegend("bottomleft", pal = forest_pal, values = ~macleish_layers[["forests"]]$Sheet1__Na, title = "Vegetation Type")
```


####Resources necessary to implement this recommendation

With our findings, Smith College and the Macleish Field Station should plan on creating more campsites over the summer. However, there are many elements to be considered beyond the placement of the campsites. First, the field station must consider the cost of the campsite. After talking to Reid Bertone-Johnson we learned that it costs around 200 dollars to build a standard tent platform and picnic table set up, and around 3,000 dollars to invest in a lean-to structure. The Field Station does not anticipate building another lean-to because of the lofty cost and labor. It would likely take a weekend to build a tent platform and picnic table, using labor from people already employed by the Center for the Environment, Ecological Design, and Sustainability. The only environmental concern is the location in proximity to a stream. The campsite should be close to a stream, but not too close as to cause erosion. The Field Station does not take run-off into account when building campsites as the area of a campsite is generally not large enough to cause any run-off issues. There are not any major roadblocks at this moment. The Field Station has the resources neccessary to build new campsites. 


[^1]: [Link to github repository](https://github.com/rmoskowitz/mp3)